Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2025-06-12 Edith Zemanick/Sweat Variability/sweat_test_analysis.qmd
added one more Na:Cl value

@@

@@

@@

- The multiclass AUC for Na:Cl is `r round(as.numeric(auc(mc_roc)),3)`. 
- The AUC for using Na:Cl to distinguish CF from non-CF was `r round(as.numeric(auc(mc_roc$rocs[[2]])),3)`
- The best threshold for distinguishing CF from non-CF (based on the Youden index) was `r round(roc_table["Cystic Fibrosis vs. Non-CF","threshold"],3)`, and provided a sensitivity of `r round(roc_table["Cystic Fibrosis vs. Non-CF","sensitivity"],3)` and specificity of `r round(roc_table["Cystic Fibrosis vs. Non-CF","specificity"],3)`

- The AUC for using Na:Cl to distinguish CF from CFTR-RD or CRMS was `r round(as.numeric(auc(mc_roc$rocs[[1]])),3)`
- The best threshold for distinguishing CF from CFTR-RD or CRMS (based on the Youden index) was `r round(roc_table["CFTR-RD or CRMS vs. Cystic Fibrosis","threshold"],3)`, and provided a sensitivity of `r round(roc_table["CFTR-RD or CRMS vs. Cystic Fibrosis","sensitivity"],3)` and specificity of `r round(roc_table["CFTR-RD or CRMS vs. Cystic Fibrosis","specificity"],3)`

- The AUC for using Na:Cl to distinguish non-CF from CFTR-RD or CRMS was `r round(as.numeric(auc(mc_roc$rocs[[3]])),3)`
- The best threshold for distinguishing CF from CFTR-RD or CRMS (based on the Youden index) was `r round(roc_table["CFTR-RD or CRMS vs. Non-CF","threshold"],3)`, and provided a sensitivity of `r round(roc_table["CFTR-RD or CRMS vs. Non-CF","sensitivity"],3)` and specificity of `r round(roc_table["CFTR-RD or CRMS vs. Non-CF","specificity"],3)`

>>>>

chco$Na_Right[790] <- 21.1
chco$Na_Left[790] <- 24.1

@@

# Change Cl under 10 to 9 per CHEC
df$Cl[df$Cl < 10] <- 9
df$Na[df$Na < 10] <- 9

@@

# Additional lists for Angela
write.csv(
  df %>%
    filter(Diagnosis == "Non-CF" & Cl >= 60),
  file = "./Data_Cleaned/sweat_variability_non_cf_cl_60.csv",
write.csv(
  df %>%
    filter(Diagnosis == "Cystic Fibrosis" & `Na:Cl` >= 1.2),
  file = "./Data_Cleaned/sweat_variability_cf_nacl_1_2.csv",
write.csv(
  df %>%
    filter(Diagnosis == "Non-CF" & `Na:Cl` < 1.2),
  file = "./Data_Cleaned/sweat_variability_non_cf_nacl_1_2.csv",

@@

- The multiclass AUC for Na:Cl is `r round(as.numeric(auc(mc_roc)),3)`.
